### 2024-07-06 cognitive-bias.qmd
20240706 - epistemology

Statistical analysis—and science more generally—is a process to the pursuit of knowledge.
Science is perhaps the best tool that society has to approximate the truth.
It relies on empirical evidence and does not give undue weight to anecdotal evidence, intuition, tradition, or authority.
Nevertheless, statistical analysis is not purely objective and is not a panacea.
Science is a human enterprise—it is performed by humans each of whom has their own biases.
For instance, cognitive biases can influence how people interpret statistics.
As a result, the findings from any given study may be incorrect.
Thus, it would be imprudent to make decisions based solely on the results of one study.
That is why we wait for findings to be independently replicated by different groups of researchers using different methods.

>>>>

Statistical analysis—and science more generally—is a process to the pursuit of knowledge.
An *epistemology* is an approach to knowledge.
Science is perhaps the best approach (epistemology) that society has to approximate truth.
Unlike other approaches to knowledge, science relies on empirical evidence and does not give undue weight to anecdotal evidence, intuition, tradition, or authority.
Nevertheless, statistical analysis is not purely objective and is not a panacea.
Science is a human enterprise—it is performed by humans each of whom has their own biases.
For instance, cognitive biases can influence how people interpret statistics.
As a result, the findings from any given study may be incorrect.
Thus, it would be imprudent to make decisions based solely on the results of one study.
That is why we wait for findings to be independently replicated by different groups of researchers using different methods.
